lab_notebook

### 2018-11-09 lab_notebook.Rmd
load edf data
- merged turf data into projection/ITQ datafram. issue: only 2 species from the edf data set match with the projection/ITQ data. will wait and see if Gina sends any more info on TURFS

@@

>>>>

#EDF turf data
edf_turf <- read_excel("data/EDF_TURF_data.xlsx")

@@

##edf turf data wrangling
```{r}

edf_turf_unite <- edf_turf %>% unite(SciName, genus, species, sep = " ")

edf_turf_simple <- select(edf_turf_unite, "country", "start_date", "SciName")

colnames(edf_turf_simple) <- c("Country", "turfstart", "SciName")

##want to merge the edf simple with ITQ/Projections but maybe wait for Gina to respond with her TURF data
##in ITQ data says only one species of fish in japan has TURFs but not true

edf_projection_itq <- merge(ITQ_projection, edf_turf_simple, by = c("Country", "SciName"))
#only three species from the EDF data match with the species from the upside/projection data; all in Japan

Need to create new dataset (half upside half ITQ): Species, turf/itq, country,and then matching all the parameters with the species
